Dismal Code: Studying the Evolution of Security Vulnerabilities

### 2013-01-26 docs/msr.tex
added two approaches in the related work section

There are noumerous methods for mining software repositories in the context
of software evolution~\cite{KCM07}. In this section we focus on the ones
that highlight the relationship between software bugs and evolution. The key
idea behind this concept is typically similar to ours: the combination of
information like bug decriptions, documentation and others with the information
retrieved from either the source or object code of a project version.

>>>>

There are noumerous methods for mining software repositories in the context
of software evolution~\cite{KCM07}. In this section we focus on the ones
that highlight the relationship between software bugs and evolution and try to
extract useful conclusions. The key idea behind this concept is
similar to ours: the combination of information like bug decriptions,
documentation and others with the information retrieved from either the source
or object code of a project version.

{\it Refactoring identification} through software evolution is an approach used to
relate refactorings with software bugs. Weibgerber et al. found that a high
ratio of refactorings is usually followed by an increasing ratio of bug
reports~\cite{WD06}. In addition, they found that software bugs are sometimes introduced
after an incomplete refactoring~\cite{GW05}.
Ratzinger et al.~\cite{RSG08} found that the number of bugs decreases, when the number of
refactorings increases. Finally, Kim M. et al.~\cite{KCK11} showed that {\sc api}-level
refactorings aid bug fixes.

Using {\it micro patterns} is an approach proposed by Kim et al.~\cite{KPW06}
to detect bug-prone patterns among source code. Micro patterns describe programming
idioms like inheritance, data management, immutability and others. The approach involved
the examination of all revisions of three open-source projects to extract bug
introduction rates for each pattern.
